---
title: "Challenge-6"
author: "Merkayla Wong"
date: "`20-09-2023`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
<br>

#### Question-1: Countdown Blastoff (While Loop)

Create a program that simulates a rocket launch countdown using a while loop. Start from 10 and countdown to "Blastoff!" with a one-second delay between each countdown number. Print a message when the rocket launches.

**Hint:** You may want to use `cat` command to print the countdown and `Sys.sleep` for incorporating the delay

**Output preview:** Here is how the countdown could look like 

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
countdown <- function(seconds) {
  for (i in seconds:1) {
    cat(i, "\n")
    Sys.sleep(1)
  }
  cat("Blastoff!\n")
}

countdown(10)
```
<br>

#### Question-2: Word Reverser (for Loop)

Develop a program that takes a user-entered word and uses a while loop to print the word's characters in reverse order. For example, if the user enters "hello," the program should print "olleh."

**Hint:** You may want to use `substr` command to access each character of the input word, and `paste` command to join the reversed letters one at a time

**Solutions:** 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
Wordreverser <- function(word) {
  reversed <- ""
  index <- nchar(word)
  
  while (index > 0) {
    reversed <- paste(reversed, substr(word, index, index), sep = "")
    index <- index - 1
  }
  
  return(reversed)
}

word <- readline("Enter a word: ")

reversed_word <- Wordreverser(word)
cat("Reversed word:", reversed_word, "\n")
```
<br>
